Modelling the City of Melbourne Pedestrian Data

### 2017-10-03 presentation/final.Rmd
update

>>>>

---
## Specification of imputation models:
Model at sensors with small proportion of missing values
$$E[HourlyCounts_{sensor, t}|.] = \exp \{ \beta_{0, sensor} + \sum_{j = 1}^{11}(\beta_{1,j,sensor}Month^j_{t}) + \sum_{k = 1}^{23}(\beta_{2,k,sensor}Time_{t})$$

$$+\sum_{l = 1}^{5}(\beta_{3,l,sensor}DayType_t) + \sum_{k = 1}^{23} \sum_{l = 1}^{5} (\beta_{4,k,l,sensor}Time_t DayType_t) \} \qquad \forall \mathtt{NA}_{prop}(sensor) < \mathtt{threshold}$$
